The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-04-16 paper/ms.tex
sent to coauthors

\title{The Abundance of Bullet Groups in $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
  G.Foex$^4$, T. Verdugo$^3$ and V. Motta$^4$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela\\
  $^4$ Instituto de F\'isica y Astronom\'ia, Universidad de
  Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
  2360102, Chile  
}
\email{jfernandezt87@gmail.com}
\email{je.forero@uniandes.edu.co}
\begin{abstract}

@@

Using a Sheth-Mo-Tormen mass function at $z=0$, one can estimate that
systems around this mass are $\sim 65$ times more abundant than massive
clusters in the mass range of the Bullet Cluster $>10^{15}$\hMsun
\citep{Sheth2001,hmfcalc}. This  should open up the possibility of
finding Bullet-like groups in large numbers to test
$\Lambda$CDM. However, a larger abundance of small mass systems has to
be weighted by the probability of being in a merger and  presenting a
large displacement between the DM and gaseous components.  These two
conditions (merger rates, maximum possible displacement) are a funcion
of DM halo mass in $\Lambda$CDM cosmologies.  A detailed statistical
study to estimate the DM-gas displacements of bullets has been
performed for clusters \citep{ForeroRomero2010} but not for lower mass
systems.

@@

Bullet-like configurations have two dominant dark matter structures:
the host halo and the dominant sub-halo. We describe the kinematics of
this configuration by the  position and velocity vectors of the
sub-halo in a frame of reference where the main halo is at rest; thus
$\vec{v{}}=\vec{v}_{\rm sub}-\vec{v}_{\rm host}$ and
$\vec{r{}}=\vec{r}_{\rm sub}-\vec{r}_{\rm host}$, where the subscripts $host$
and $sub$ refer to the host and sub-halo, respectively. The positions
$\vec{r}$ correspond to the minium of potential and the velocities
$\vec{v}$ are computed as an average of the bulk velocities of all
simulation particles in the structure of interest.

The angle between these two vectors can be quantified by, 
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} .
 \end{equation} 
%
This encondes information about the collision, i.e. cases of
$|\mu|\sim 1$ can be considered as head-on collisions while
$|\mu|< 0.9$ describes a grazing trajectory.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_2.pdf}
\end{center}
\caption{2D histograms in the plane $\mu$-$D_{\rm off}$ describing the
  geometry of the bullet encounter. The left
  panel corresponds to clusters and the right panel to groups. 
  The weak redshift evolution of the structure in these planes
  allows us to include halos at all redshifts to construct these figures.
  The three rectangles (continous, dashed, dashed-dotted)
  delimit stages of interest in a head-on collision as described in
  Section \ref{sec:geometry}.}
\label{fig:geometry}
\end{figure*}

Figure \ref{fig:geometry} presents the geometry of the intereactions using the 
variables $\mu$ and $D_{\rm off}$. The first evident feature is that
most of the configurations have head-on encouters, $|\mu|>0.9$
($\theta\leq 30^{\circ}$), while only a minority with $|\mu|<0.9$ can
be described as having  grazing trajectories.

For pairs on radial trajectories there are three regions of interest
in this plane that correspond to the three merging stages described
at the end of Section \ref{sec:geometry} assuming that the sub-halo
merges (or falls below the BDM detection threshold) right at its
second pass through the center of the host halo \citep{Poole2006}.
These regions are shown as three different rectangled in Figure
\ref{fig:geometry}.

@@

Our estimates are based on the different kinds of trajectories and
collision stages described in previous sections. To start with, we
consider that systems with $|\mu|<0.9$ describing grazing
trajectories have a DM-gas displacement equal to zero.  In systems
with head-on collissions, $|\mu|>0.9$ the systems with $\mu<-0.9$ and
large displacements $D_{\rm   off}>0.6$ most probably describe the
beginning of the interaction and should have DM-gas displacements
equal to zero as well. In all other cases the DM-gas displacement
should be different from zero with the approximated value
$d_{\rm   2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
the offset computed between the minium of potential and the center of
mass for each host halo computed from all the matter inside the virial
radius.

@@

Recently \cite{Foex2013} presented an analysis of $80$ galaxy groups
in the SL2S sample. From the light distribution, only $34$ objects
($\sim 42\%$) have regular isophotes, $33$ had ellongated
isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
clear bi-modal light distribution; \bullg\ is one of these
$13$ systems.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{figure_3.pdf}
\end{center}
\caption{Integrated probability distribution for the estimated
  DM-gas displacements in the group and cluster samples. Continous (dashed)
  lines correspond to clusters (groups). The continuous black line
  marked as $P_{2D}$ shows the statistics reported by
  \citet{ForeroRomero2010} for a cosmological simulation including DM
  and gas. The vertical lines correspond to the mean value and
  uncertainty of the displacement measured for \bullg.} 
\label{fig:baryonic_displacements}
\end{figure*}

@@

Using the same criteria we find that in the simulation there are
$\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ groups similar to \bullg. This
number density is three times larger than the computed value for
clusters. This opens up a new observational possibility with surveys
such as SL2S that target a large number of groups and estimate its
multi-modal nature from lensing analysis \citep{Foex2013}. An approach
that can be further exploited with upcoming lensing surveys (e.g. with
 he {\it Euclid} satellite) and pushes for X-ray surveys with higher
sensibility: chances are larger to find bullets in systems with lower
X-ray luminosities.

@@

We thank the referee for a report that improved the readibility of our
results. 
J.E.F-R acknowledges support from Vicerrector\'ia de
Investigaciones through a FAPA starting grant.

@@

@@

\bibliographystyle{apj}
\bibliography{references}

>>>>

\title{The abundance of Bullet-Groups in $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
  G.Foex$^4$, T. Verdugo$^3$ and V. Motta$^4$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela\\
  $^4$ Instituto de F\'isica y Astronom\'ia, Universidad de
  Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
  2360102, Chile  
}
\email{jfernandezt87@gmail.com}
\email{je.forero@uniandes.edu.co}
\begin{abstract}

@@

Using a Sheth-Mo-Tormen mass function at $z=0$, one can estimate that
systems around this mass are $\sim 65$ times more abundant than massive
clusters in the mass range of the Bullet Cluster $>10^{15}$\hMsun
\citep{Sheth2001,hmfcalc}. This  should open up the possibility of
finding Bullet-like groups in large numbers to test
$\Lambda$CDM. However, a larger abundance of small mass systems has to
be weighted by the probability of being in a merger and  presenting a
large displacement between the DM and gaseous components.  These two
conditions (merger rates, maximum possible displacement) are a function
of DM halo mass in $\Lambda$CDM cosmologies.  A detailed statistical
study to estimate the DM-gas displacements of bullets has been
performed for clusters \citep{ForeroRomero2010} but not for lower mass
systems.

@@

Bullet-like configurations have two dominant dark matter structures:
the host halo and the dominant sub-halo. We describe the kinematics of
this configuration by the  position and velocity vectors of the
sub-halo in a frame of reference where the main halo is at rest; thus
$\vec{v{}}=\vec{v}_{\rm sub}-\vec{v}_{\rm host}$ and
$\vec{r{}}=\vec{r}_{\rm sub}-\vec{r}_{\rm host}$, where the subscripts $host$
and $sub$ refer to the host and sub-halo, respectively. The positions
$\vec{r}$ correspond to the minimum of potential and the velocities
$\vec{v}$ are computed as an average of the bulk velocities of all
simulation particles in the structure of interest.

The angle between these two vectors can be quantified by, 
\begin{equation}
  \mu\equiv
  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
    \left\|\vec{r}\right\|} .
 \end{equation} 
%
This encodes information about the collision, i.e. cases of
$|\mu|\sim 1$ can be considered as head-on collisions while
$|\mu|< 0.9$ describes a grazing trajectory.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_2.pdf}
\end{center}
\caption{2D histograms in the plane $\mu$-$D_{\rm off}$ describing the
  geometry of the bullet encounter. The left
  panel corresponds to clusters and the right panel to groups. 
  The weak redshift evolution of the structure in these planes
  allows us to include halos at all redshifts to construct these figures.
  The three rectangles (continuous, dashed, dashed-dotted)
  delimit stages of interest in a head-on collision as described in
  Section \ref{sec:geometry}.}
\label{fig:geometry}
\end{figure*}

Figure \ref{fig:geometry} presents the geometry of the interactions using the 
variables $\mu$ and $D_{\rm off}$. The first evident feature is that
most of the configurations have head-on encounters, $|\mu|>0.9$
($\theta\leq 30^{\circ}$), while only a minority with $|\mu|<0.9$ can
be described as having  grazing trajectories.

For pairs on radial trajectories there are three regions of interest
in this plane that correspond to the three merging stages described
at the end of Section \ref{sec:geometry} assuming that the sub-halo
merges (or falls below the BDM detection threshold) right at its
second pass through the center of the host halo \citep{Poole2006}.
These regions are shown as three different rectangles in Figure
\ref{fig:geometry}.

@@

Our estimates are based on the different kinds of trajectories and
collision stages described in previous sections. To start with, we
consider that systems with $|\mu|<0.9$ describing grazing
trajectories have a DM-gas displacement equal to zero.  In systems
with head-on collisions, $|\mu|>0.9$ the systems with $\mu<-0.9$ and
large displacements $D_{\rm   off}>0.6$ most probably describe the
beginning of the interaction and should have DM-gas displacements
equal to zero as well. In all other cases the DM-gas displacement
should be different from zero with the approximated value
$d_{\rm   2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
the offset computed between the minimum of potential and the center of
mass for each host halo computed from all the matter inside the virial
radius.

@@

Recently \cite{Foex2013} presented an analysis of $80$ galaxy groups
in the SL2S sample. From the light distribution, only $34$ objects
($\sim 42\%$) have regular isophotes, $33$ had elongated
isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
clear bi-modal light distribution; \bullg\ is one of these
$13$ systems.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{figure_3.pdf}
\end{center}
\caption{Integrated probability distribution for the estimated
  DM-gas displacements in the group and cluster samples. Continuous (dashed)
  lines correspond to clusters (groups). The continuous black line
  marked as $P_{2D}$ shows the statistics reported by
  \citet{ForeroRomero2010} for a cosmological simulation including DM
  and gas. The vertical lines correspond to the mean value and
  uncertainty of the displacement measured for \bullg.} 
\label{fig:baryonic_displacements}
\end{figure*}

@@

Using the same criteria we find that in the simulation there are
$\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ groups similar to \bullg. This
number density is three times larger than the computed value for
clusters. This opens up a new observational possibility with surveys
such as SL2S that target a large number of groups and estimate its
multi-modal nature from lensing analysis \citep{Foex2013}. An approach
that can be further exploited with upcoming lensing surveys (e.g. with
 he {\it Euclid} satellite) and pushes for X-ray surveys with higher
sensibility: chances are larger to find bullets in systems with lower
X-ray luminosities.\\

We thank the referee for a detailed report that improved the readability of
this Letter.

@@

@@

J.E.F-R acknowledges support from Vicerrector\'ia de
Investigaciones through a FAPA starting grant.

@@

\bibliographystyle{apj}
%\bibliography{references} 
\begin{thebibliography}{28}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Brada{\v c}} {et~al.}(2008){Brada{\v c}}, {Allen}, {Treu},
  {Ebeling}, {Massey}, {Morris}, {von der Linden}, \& {Applegate}}]{Bradac2008}
{Brada{\v c}}, M., {Allen}, S.~W., {Treu}, T., {Ebeling}, H., {Massey}, R.,
  {Morris}, R.~G., {von der Linden}, A., \& {Applegate}, D. 2008, \apj, 687,
  959

\bibitem[{{Cabanac} {et~al.}(2007){Cabanac}, {Alard}, {Dantel-Fort}, {Fort},
  {Gavazzi}, {Gomez}, {Kneib}, {Le F{\`e}vre}, {Mellier}, {Pello}, {Soucail},
  {Sygnet}, \& {Valls-Gabaud}}]{Cabanac2007}
{Cabanac}, R.~A., {Alard}, C., {Dantel-Fort}, M., {Fort}, B., {Gavazzi}, R.,
  {Gomez}, P., {Kneib}, J.~P., {Le F{\`e}vre}, O., {Mellier}, Y., {Pello}, R.,
  {Soucail}, G., {Sygnet}, J.~F., \& {Valls-Gabaud}, D. 2007, \aap, 461, 813

\bibitem[{{Clowe} {et~al.}(2006){Clowe}, {Brada{\v c}}, {Gonzalez},
  {Markevitch}, {Randall}, {Jones}, \& {Zaritsky}}]{Clowe2006}
{Clowe}, D., {Brada{\v c}}, M., {Gonzalez}, A.~H., {Markevitch}, M., {Randall},
  S.~W., {Jones}, C., \& {Zaritsky}, D. 2006, \apjl, 648, L109

\bibitem[{{Dahle} {et~al.}(2013){Dahle}, {Sarazin}, {Lopez}, {Kouveliotou},
  {Patel}, {Rol}, {van der Horst}, {Fynbo}, {Wijers}, {Burrows}, {Gehrels},
  {Grupe}, {Ramirez-Ruiz}, \& {Micha{\l}owski}}]{Dahle2013}
{Dahle}, H., {Sarazin}, C.~L., {Lopez}, L.~A., {Kouveliotou}, C., {Patel},
  S.~K., {Rol}, E., {van der Horst}, A.~J., {Fynbo}, J., {Wijers}, R.~A.~M.~J.,
  {Burrows}, D.~N., {Gehrels}, N., {Grupe}, D., {Ramirez-Ruiz}, E., \&
  {Micha{\l}owski}, M.~J. 2013, \apj, 772, 23

\bibitem[{{Dawson} {et~al.}(2012){Dawson}, {Wittman}, {Jee}, {Gee}, {Hughes},
  {Tyson}, {Schmidt}, {Thorman}, {Brada{\v c}}, {Miyazaki}, {Lemaux}, {Utsumi},
  \& {Margoniner}}]{Dawson2012}
{Dawson}, W.~A., {Wittman}, D., {Jee}, M.~J., {Gee}, P., {Hughes}, J.~P.,
  {Tyson}, J.~A., {Schmidt}, S., {Thorman}, P., {Brada{\v c}}, M., {Miyazaki},
  S., {Lemaux}, B., {Utsumi}, Y., \& {Margoniner}, V.~E. 2012, \apjl, 747, L42

\bibitem[{{Farrar} \& {Rosen}(2007)}]{Farrar2007}
{Farrar}, G.~R., \& {Rosen}, R.~A. 2007, Physical Review Letters, 98, 171302

\bibitem[{{Fo{\"e}x} {et~al.}(2013){Fo{\"e}x}, {Motta}, {Limousin}, {Verdugo},
  {More}, {Cabanac}, {Gavazzi}, \& {Mu{\~n}oz}}]{Foex2013}
{Fo{\"e}x}, G., {Motta}, V., {Limousin}, M., {Verdugo}, T., {More}, A.,
  {Cabanac}, R., {Gavazzi}, R., \& {Mu{\~n}oz}, R.~P. 2013, \aap, 559, A105

\bibitem[{{Forero-Romero} {et~al.}(2010){Forero-Romero}, {Gottl{\"o}ber}, \&
  {Yepes}}]{ForeroRomero2010}
{Forero-Romero}, J.~E., {Gottl{\"o}ber}, S., \& {Yepes}, G. 2010, \apj, 725,
  598

\bibitem[{{Gastaldello} {et~al.}(2014){Gastaldello}, {Limousin}, {Foex},
  {Mu\~noz}, {Verdugo}, {Motta}, {More}, {Cabanac}, {Buote}, {Eckert},
  {Ettori}, {Fritz}, {Ghizzardi}, {Humphrey}, {Meneghetti}, \&
  {Rossetti}}]{Gastaldello}
{Gastaldello}, F., {Limousin}, M., {Foex}, G., {Mu\~noz}, R., {Verdugo}, T.,
  {Motta}, V., {More}, A., {Cabanac}, R., {Buote}, D., {Eckert}, D., {Ettori},
  S., {Fritz}, A., {Ghizzardi}, S., {Humphrey}, P., {Meneghetti}, M., \&
  {Rossetti}, M. 2014, \mnras\ accepted

\bibitem[{{Hayashi} \& {White}(2006)}]{Hayashi2006}
{Hayashi}, E., \& {White}, S.~D.~M. 2006, \mnras, 370, L38

\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
  \& {Wright}}]{hinshaw_etal13}
{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
  {Wright}, E.~L. 2013, \apjs, 208, 19

\bibitem[{{Klypin} {et~al.}(1999){Klypin}, {Gottl{\"o}ber}, {Kravtsov}, \&
  {Khokhlov}}]{BDMb}
{Klypin}, A., {Gottl{\"o}ber}, S., {Kravtsov}, A.~V., \& {Khokhlov}, A.~M.
  1999, \apj, 516, 530

\bibitem[{{Klypin} \& {Holtzman}(1997)}]{BDM}
{Klypin}, A., \& {Holtzman}, J. 1997, ArXiv Astrophysics e-prints

\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
  {Primack}}]{2011ApJ...740..102K}
{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102

\bibitem[{{Kravtsov} {et~al.}(1997){Kravtsov}, {Klypin}, \&
  {Khokhlov}}]{Kravtsov1997}
{Kravtsov}, A.~V., {Klypin}, A.~A., \& {Khokhlov}, A.~M. 1997, \apjs, 111, 73

\bibitem[{{Lee} \& {Baldi}(2012)}]{Lee2012}
{Lee}, J., \& {Baldi}, M. 2012, \apj, 747, 45

\bibitem[{{Lee} \& {Komatsu}(2010)}]{Lee2010}
{Lee}, J., \& {Komatsu}, E. 2010, \apj, 718, 60

\bibitem[{{Markevitch} {et~al.}(2004){Markevitch}, {Gonzalez}, {Clowe},
  {Vikhlinin}, {Forman}, {Jones}, {Murray}, \& {Tucker}}]{Markevitch2004}
{Markevitch}, M., {Gonzalez}, A.~H., {Clowe}, D., {Vikhlinin}, A., {Forman},
  W., {Jones}, C., {Murray}, S., \& {Tucker}, W. 2004, \apj, 606, 819

\bibitem[{{Mastropietro} \& {Burkert}(2008)}]{Mastropietro2008}
{Mastropietro}, C., \& {Burkert}, A. 2008, \mnras, 389, 967

\bibitem[{{Merten} {et~al.}(2011){Merten}, {Coe}, {Dupke}, {Massey}, {Zitrin},
  {Cypriano}, {Okabe}, {Frye}, {Braglia}, {Jim{\'e}nez-Teja}, {Ben{\'{\i}}tez},
  {Broadhurst}, {Rhodes}, {Meneghetti}, {Moustakas}, {Sodr{\'e}}, {Krick}, \&
  {Bregman}}]{Merten2011}
{Merten}, J., {Coe}, D., {Dupke}, R., {Massey}, R., {Zitrin}, A., {Cypriano},
  E.~S., {Okabe}, N., {Frye}, B., {Braglia}, F.~G., {Jim{\'e}nez-Teja}, Y.,
  {Ben{\'{\i}}tez}, N., {Broadhurst}, T., {Rhodes}, J., {Meneghetti}, M.,
  {Moustakas}, L.~A., {Sodr{\'e}}, Jr., L., {Krick}, J., \& {Bregman}, J.~N.
  2011, \mnras, 417, 333

\bibitem[{{Milosavljevi{\'c}} {et~al.}(2007){Milosavljevi{\'c}}, {Koda},
  {Nagai}, {Nakar}, \& {Shapiro}}]{Milosavljevic2007}
{Milosavljevi{\'c}}, M., {Koda}, J., {Nagai}, D., {Nakar}, E., \& {Shapiro},
  P.~R. 2007, \apjl, 661, L131

\bibitem[{{More} {et~al.}(2012){More}, {Cabanac}, {More}, {Alard}, {Limousin},
  {Kneib}, {Gavazzi}, \& {Motta}}]{More2012}
{More}, A., {Cabanac}, R., {More}, S., {Alard}, C., {Limousin}, M., {Kneib},
  J.-P., {Gavazzi}, R., \& {Motta}, V. 2012, \apj, 749, 38

\bibitem[{{Murray} {et~al.}(2013){Murray}, {Power}, \& {Robotham}}]{hmfcalc}
{Murray}, S.~G., {Power}, C., \& {Robotham}, A.~S.~G. 2013, Astronomy and
  Computing, 3, 23

\bibitem[{{Poole} {et~al.}(2006){Poole}, {Fardal}, {Babul}, {McCarthy},
  {Quinn}, \& {Wadsley}}]{Poole2006}
{Poole}, G.~B., {Fardal}, M.~A., {Babul}, A., {McCarthy}, I.~G., {Quinn}, T.,
  \& {Wadsley}, J. 2006, \mnras, 373, 881

\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
  {Turchaninov}}]{Riebe2013}
{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691

\bibitem[{{Sheth} {et~al.}(2001){Sheth}, {Mo}, \& {Tormen}}]{Sheth2001}
{Sheth}, R.~K., {Mo}, H.~J., \& {Tormen}, G. 2001, \mnras, 323, 1

\bibitem[{{Springel} \& {Farrar}(2007)}]{Springel2007}
{Springel}, V., \& {Farrar}, G.~R. 2007, \mnras, 380, 911

\bibitem[{{Thompson} \& {Nagamine}(2012)}]{Thompson2012}
{Thompson}, R., \& {Nagamine}, K. 2012, \mnras, 419, 3560

\end{thebibliography}
